### 2019-11-07 report/paper.tex
fix images in paper

\section{Conclusion}
In this project, we used several computer vision techniques and algorithms that we had
learnt in class, and put them into practice. Though our solution needs further work on the dismissal of
false positives, we manage to detect several instances of the characters of interest. By trying several
classification approaches simultaneously in the beginning of the project phase, we were able to reject those
which were less promising and could therefore concentrate our energy on improving the algorithm providing
the best results. The pursue of the idea to combine two feature descriptors lead to a significant increase
of the average performance of our classifier.

>>>>

\section{Conclusion}
\begin{figure}
    \centering
    \begin{subfigure}{0.45\linewidth}
    \includegraphics[width=\linewidth]{figures/detections_2}
    \end{subfigure}
    \begin{subfigure}{0.45\linewidth}
    \includegraphics[width=\linewidth]{figures/detections_3}
    \end{subfigure}
    \caption{Detection on full size images of the validation set. Ground truth is shown in green, detections in red.}
    \label{fig:detections-img}
\end{figure}

In this project, we used several computer vision techniques and algorithms that we had
learnt in class, and put them into practice. Though our solution needs further work (see \autoref{fig:detections-img}) on the dismissal of
false positives, we manage to detect several instances of the characters of interest. By trying several
classification approaches simultaneously in the beginning of the project phase, we were able to reject those
which were less promising and could therefore concentrate our energy on improving the algorithm providing
the best results. The pursue of the idea to combine two feature descriptors lead to a significant increase
of the average performance of our classifier.
